\chapter{Discussion}
\label{Discussion}

\section{Summary of Key Findings}

In this study, I conducted a series of experiments to evaluate the performance of different GAN architectures and explored various factors influencing the quality of generated images. Specifically, I compared the effects of using dense layers versus convolutional layers in a standard GAN, examined the impact of varying the number of convolutional layers in the generator and discriminator, analyzed the effects of data augmentation on GAN training, and ultimately applied a GAN model to a new dataset to generate high-quality cat face images.

\section{Impact of Model Structure}

The experiments revealed that GAN models utilizing convolutional layers significantly outperformed those using dense layers in terms of image quality. This finding aligns with the well-established ability of convolutional layers to capture spatial features in images. Further experiments demonstrated that increasing the number of layers in either the generator or the discriminator individually led to decreased model performance. This imbalance disrupts the dynamic equilibrium between the generator and discriminator in the GAN framework, underscoring the importance of maintaining this balance during GAN training.

\section{Data Augmentation Effects}

The updated experimental results indicate that data augmentation generally led to lower optimization performance. Although data augmentation typically enhances a model’s generalization ability, in this study, it may have introduced excessive noise, interfering with the GAN training process. This suggests that the careful selection of augmentation methods and parameters is crucial to avoid destabilizing the model and hindering convergence. Therefore, when training GANs, the use of data augmentation should be approached with caution to prevent negative impacts on model performance.

\section{Performance on New Dataset}

When applying the model to the high-resolution Animal Faces-HQ dataset, I successfully trained a standard GAN model to generate realistic cat images. This result validates the effectiveness of standard GANs in handling high-resolution images and demonstrates the potential of GANs in generating realistic images. However, due to hardware constraints, I had to downscale the images from 512x512 pixels to 128x128 pixels, which may have limited the final quality of the generated images.

\section{Limitations and Future Work}

Despite the positive outcomes, this study has some limitations. Firstly, due to limited computational resources, I was unable to train the model on higher-resolution images, which may have affected the quality of the generated images. Secondly, my experiments primarily focused on standard GANs and their simple variants; future research could explore more advanced GAN variants such as StyleGAN or BigGAN. Additionally, in the area of data augmentation, further research is needed to design more effective augmentation strategies that can improve GAN training efficiency and the quality of generated images.

In future work, I plan to optimize the data augmentation strategies and attempt training on higher-resolution images. Furthermore, exploring different types of GAN models, such as Conditional GANs or Adaptive GANs, to enhance the diversity and quality of generated images could be valuable.

\section{Conclusion}

Overall, this study provides a comprehensive analysis of GAN performance through a series of experiments, demonstrating its potential in generating high-quality images. Despite some challenges, GANs remain a powerful tool in the field of generative models, and future improvements and optimizations are expected to further enhance their applicability.